Unifying Lower Bounds on Prediction Dimension of Consistent Convex Surrogates

### 2021-01-27 colt-21/cvx-flats.tex
cHANGING FIGURE 1 TO BE A TABLE WITH EXAMPLES

\begin{figure}
	\begin{minipage}{0.25\linewidth}
	\caption{The four quadrants of prediction tasks; Theorem~\ref{thm:consistent-implies-indir-elic} allows us to understand the relationship between indirect elicitation and consistency in all four quadrants for the first time.}\label{fig:four-quadrants}	
	\end{minipage}
	\hfill
	\begin{minipage}{0.72\linewidth}
	\centering
	\includegraphics[width=0.95\linewidth]{tikz/consistency-elicitation-calibration.pdf}
	\end{minipage}
\end{figure}

@@

Various works have studied the minimum prediction dimension $d$ needed in order to construct a consistent surrogate loss $L: \reals^d \times \Y \to \reals$, typically through proxies such as calibration~\citep{steinwart2008support,agarwal2015consistent,ramaswamy2016convex} and property elicitation~\citep{frongillo2015vector-valued,fissler2016higher,frongillo2018elicitation}.
\raft{Nice!  Love ``proxies'' here.}
For discrete target losses, \citet{ramaswamy2016convex} introduce \emph{convex calibration dimension}, the minimum prediction dimension yielding a convex calibrated surrogate.\jessiet{Discussion about how this is really about consistency}
Their results have led to the design of consistent convex surrogates for discrete prediction problems such as hierarchical classification~\citep{ramaswamy2015hierarchical} and classification with an abstain option~\citep{ramaswamy2018consistent}.

\raft{FYI Jessie: Two general points.  (1) I spent the majority of my time in this section just on dependencies; e.g.\ you had ``similar to elicitation complexity mentioned above'' but elicitation complexity was not mentioned above.  Next time it would be more efficient if you made sure to balance local edits with global scans to catch these sorts of things, as well as making sure we aren't explaining things twice, etc.  (2) You tend to mix background with nods to our results, which is actually good to do, but it can be jarring if you go back and forth too much.  See for example how I changed the previous subsection, reserving the nod to our work to the end of the subsection.}\jessiet{Noted boss man}

@@

\jessiet{Simplify; merge with Sec 4.  Jessie take a pass at proof sketch of Theorem 1.  Narrative here reads to me as ``hey this general result through calibration is our main contribution'' which I'm not sure if we particularly want.  Also want to double check how different our calibration definition is from Steinwart}

>>>>

%\begin{figure}
%	\begin{minipage}{0.25\linewidth}
%	\caption{The four quadrants of prediction tasks; Theorem~\ref{thm:consistent-implies-indir-elic} allows us to understand the relationship between indirect elicitation and consistency in all four quadrants for the first time.}\label{fig:four-quadrants}	
%	\end{minipage}
%	\hfill
%	\begin{minipage}{0.72\linewidth}
%	\centering
%	\includegraphics[width=0.95\linewidth]{tikz/consistency-elicitation-calibration.pdf}
%	\end{minipage}
%\end{figure}

\begin{table}
	\begin{center}
	\begin{tabular}{|l||l|l|} 
		\hline
		& \emph{Target loss}  & \emph{Target statistic}\\ \hline \hline
		\emph{Discrete prediction} & \textbf{Q1:} High-confidence classification \S~\ref{sec:finite-calib}  & \textbf{Q2:} Hierarchical prediction App.~\ref{app:omitted-examples}\\ \hline 
		\emph{Continuous estimation} & \textbf{Q3:} AUC Optimization \jessie{??} & \textbf{Q4:} Variance, entropy, and norms \S~\ref{sec:contin-consis} \\ 
		& \cite{gao2012consistency} & \\
		\hline
	\end{tabular}
\caption{The four quadrants of problem types, with an example of interest for each.}
\label{tab:quadrants}
\end{center}
\end{table}

@@

Various works have studied the minimum prediction dimension $d$ needed in order to construct a consistent surrogate loss $L: \reals^d \times \Y \to \reals$, typically through proxies such as calibration~\citep{steinwart2008support,agarwal2015consistent,ramaswamy2016convex} and property elicitation~\citep{frongillo2015vector-valued,fissler2016higher,frongillo2018elicitation}.
%\raft{Nice!  Love ``proxies'' here.}
For discrete target losses, \citet{ramaswamy2016convex} introduce \emph{convex calibration dimension}, the minimum prediction dimension yielding a convex calibrated surrogate.\jessiet{Discussion about how this is really about consistency}
Their results have led to the design of consistent convex surrogates for discrete prediction problems such as hierarchical classification~\citep{ramaswamy2015hierarchical} and classification with an abstain option~\citep{ramaswamy2018consistent}.

%\raft{FYI Jessie: Two general points.  (1) I spent the majority of my time in this section just on dependencies; e.g.\ you had ``similar to elicitation complexity mentioned above'' but elicitation complexity was not mentioned above.  Next time it would be more efficient if you made sure to balance local edits with global scans to catch these sorts of things, as well as making sure we aren't explaining things twice, etc.  (2) You tend to mix background with nods to our results, which is actually good to do, but it can be jarring if you go back and forth too much.  See for example how I changed the previous subsection, reserving the nod to our work to the end of the subsection.}\jessiet{Noted boss man}

@@

\jessiet{Simplify; merge with Sec 4?  Narrative here reads to me as ``hey this general result through calibration is our main contribution'' which I'm not sure if we particularly want.}
